% Change the following title and label as desired.
\section{Conclusion}
\label{sec:conclusion}

% Modify the paragraphs in this section as desired.

Based on the testing results, the following conclusions can be drawn:

\begin{enumerate}
  \item The model demonstrates high detection performance with an mAP score of 81.85\% at a 0.5 threshold.
  \item The system is capable of processing frames in real-time with an average FPS of around 40, indicating adequate processing speed for field applications.
  \item The time regulator testing shows that 66.17\% of responses are within a relatively short time, but 34\% exceed 0.5 seconds.
  \item The system successfully locked the target (Locked Detection) 4 times out of 15 trials, resulting in a success rate of 26.67\%.
  \item The system performs best under optimal lighting conditions, but performance degrades under low lighting conditions.
  \item The system consistently detects objects within a distance of less than 1 meter and sends a "Stop" instruction to prevent collisions.
  \item The system exhibits excellent performance in detecting and following objects in various scenarios, whether in-frame, moving forward, or turning.
  \item The system is able to follow objects well in all tested path conditions, achieving a success rate of 100\%.
\end{enumerate}

\section{Suggestions}
\label{chap:suggestions}

For further development in future research, the following suggestions can be given:

\begin{enumerate}
  \item Improve the \texttt{track()} function to maintain the consistency of detected object ID identities, in order to enhance tracking accuracy.
  \item Consider using additional lighting that does not cause overexposure to improve detection performance under low lighting conditions.
  \item Further optimize the system to reduce response times exceeding 0.5 seconds, to enhance stability and performance consistency.
  \item Develop a more adaptive algorithm to handle out-of-frame conditions, to prevent the issuance of irrelevant or unsafe instructions.
  \item Implement the system in real-world scenarios with various operational conditions to test and ensure the overall reliability and safety of the system.
\end{enumerate}

